\chapter{User guide: command line interfaces}
\label{chap:clis}

The Astec distribution contains 4 sub-directories

\mbox{}
\dirtree{%
.1 path/to/astec/.
.2 documentation/.
.2 src/.
.2 tutorial/.
}
\mbox{}

\begin{itemize}
\itemsep -0.5ex
\item \texttt{documentation/} contains this documentation
\item \texttt{src/} contains the command line interfaces (CLIs)  and the code.
\item \texttt{tutorial/} contains a tutorial (see chap. \ref{chap:tutorial}) along with a toy example.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Data organization}

It is assumed that there will be one directory per experiment. This
directory contains the acquired data, but will also contain the result
data as depicted below. See section \ref{sec:cli:parameters:data} for more details.

\mbox{}
\dirtree{%
.1 /path/to/experiment/.
.2 RAWDATA/.
.3 \ldots.
.2 FUSE/.
.3 \ldots.
.2 SEG/.
.3 \ldots.
.2 POST/.
.3 \ldots .
}
\mbox{}

\texttt{RAWDATA/} is assumed to contain the raw data (ie acquired
images from the MuViSPIM microscope), while the other subdirectories
will contain processing results.


\section{Command line interfaces common options}
\label{sec:cli:common}

\begin{description}
  \itemsep -0.5ex
\item[\texttt{-h, --help}] \mbox{}\\
  prints a help message
\item[\texttt{-p \underline{file}, --parameters \underline{file}}] \mbox{}\\\
  set the parameter file to be parsed
\item[\texttt{-e \underline{path}, --embryo-rep \underline{path}}] \mbox{}\\\
  set the
  \texttt{\underline{path}} to the directory where the
  \texttt{RAWDATA/} directory is located.
  Can also be given in the parameter file by the variable \texttt{PATH\_EMBRYO}.
\item[\texttt{-k, --keep-temporary-files}] \mbox{}\\\
  allows to keep the temporary files. Not to be routinely used.
\item[\texttt{-f, --force}] \mbox{}\\\
  forces execution, even if (temporary) result files
  are already existing
\item[\texttt{-v, --verbose}] \mbox{}\\\
  increases verboseness (both at console and in the log file)
\item[\texttt{-nv, --no-verbose}] \mbox{}\\\
  no verboseness
\item[\texttt{-d, --debug }] \mbox{}\\\
  increases debug information (in the log file)
\item[\texttt{-nd, --no-debug}] \mbox{}\\\
  no debug information
\item[\texttt{-pp, --print-param}] \mbox{}\\\
  print parameters in console and exit. A parameter file has to be provided (\texttt{-p} option). Allows to check the parameters that will be used before any processing; it is also a means to have access to the whole parameter list. 
\end{description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 1-fuse.py
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-1-fuse}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 1.5-intraregistration.py
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-1-5-intraregistration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 2-mars.py
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-2-mars}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  3-manualcorrection.py
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-3-manualcorrection.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 4-astec.py
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-4-astec}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 5-postcorrection.py
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-5-postcorrection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% X-embryoproperties.py
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-X-embryproperties.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% input segmentation
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-input-segmentation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% parameters
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{astec-cli-parameters}
